\documentclass{article}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fontspec}

\setmainfont{JetBrainsMonoNL-Regular}
\begin{document}

\title{Chain Grid - Game Design Document}
\author{}
\date{}
\maketitle

\section{Game Title: Chain Grid}
\textbf{Genre: Puzzle / Action}
\noindent
The player controls a character who is trapped in a maze and must find the exit before time runs out or before a pursuing enemy catches them. The maze becomes more difficult as the player progresses, with obstacles, traps, and environmental challenges to overcome.\\

\section{Core Mechanics}

\subsection{Character Movement}
\noindent
The player can move the character in four directions (up, down, left, right) using keyboard controls or touchscreen swipes.\\

\subsection{Time Pressure}
\noindent
The player has a set amount of time to reach the exit, adding urgency to the puzzle-solving aspect. If the time runs out, the game ends.\\

\subsection{Enemy Pursuit}
\noindent
A pursuing enemy, like a ghost or monster, is trying to catch the player. The enemy moves at a similar speed but has a unique pathfinding algorithm. If the enemy catches the player, the game ends.\\

\subsection{Maze Generation}
\noindent


\subsection{Power-ups \& Obstacles}
\noindent
Power-ups like speed boosts, time extensions, or invisibility can be collected to help the player. Obstacles such as traps, locked doors, or moving walls must be avoided or solved through actions (e.g., pressing a button to disable a trap or finding a key for locked doors).\\

\subsection{Levels and Progression}
\noindent
Each level features a new maze with increasing difficulty. New challenges like faster enemies, more complex mazes, or additional obstacles are introduced as the player advances.\\

\section{Art Style}

\subsection{Pixel Art}
\noindent
A retro, pixelated art style would work well for the game, with clean, simple designs for the character, enemies, and maze elements.\\

\subsection{Top-Down View}
\noindent
The game could be viewed from a top-down perspective, with the maze fully visible on screen and the player’s character moving through the maze.\\

\section{Win Condition}
\noindent
The player wins by escaping the maze within the time limit and without being caught by the enemy.

\section{Lose Condition}
\noindent
The game is over if the player is caught by the enemy or if time runs out.\\

\section{Unique Twist}
\noindent
The maze is dynamic, and parts of it can change as the player progresses (e.g., walls shifting, traps activating, enemies spawning). This keeps the gameplay fresh and unpredictable, making every playthrough different.\\

\end{document}
